Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-05 Cover_letter_JPM.tex
Updates from Overleaf

\section*{Cover letter for the re-submission (jpm-1174473)} 
% 2021/04/25
% 直接 online 填寫即可
%Please provide a cover letter to explain point-by-point the details of the revisions [changes 摘要即可 from the rebuttal]  in the manuscript

@@

June 30, 2021

@@

%{% A SUMMARY
Reviewer 1: % {2-4}
%"Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use."\\
We re-wrote the Introduction in detail according to the suggestion by reviewer \#2.
added new supplementary Figure S1, S2, and S3
Reviewer 2: % {3-1}
%"Are the conclusions supported by the results?
We provide more evidence by additional analysis of TCGA and GEO databases. Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
%, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 
%to provide more evidence from the significant literature review.
%}

@@

We also think that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
%=> defense: 
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來(like Figure 4: (Please see supplementary Figure SXXX))
%說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
% file: 1453 Feb 15 2020 ./intermediate_data/HNSCC_OS_marginSFP_pvalueBonferroni_KM_candidate_cox.Rda => candidate_sample
%[1] "HNSCC_OS_marginS_pvalueBonferroni_sorted"   
%[2] "HNSCC_OS_marginFree_pvalueBonferroni_sorted"
%[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 5": top 3 candidate biomarkers, CAMK2N1, CALML5, and FCGBP).
Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
supplementary figure S1). After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233}.
%Rplot_pvaluePlot_NDFIP1.pdf
%  to find cases_OS outside of range 180-220 (== cutoff not at median)
%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
%# NDFIP1 (within our 20 preliminary candidates), 
In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more potential candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
%Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
Indeed, it needs to be validated by the other independent cohort.

>>>>

\section*{Cover letter for the re-submission (jpm-1174473)} 
% 2021/04/25 to 2021/07/05
% 直接 online 填寫即可
%Please provide a cover letter to explain point-by-point the details of the revisions [changes 摘要即可 from the rebuttal]  in the manuscript

@@

July 05, 2021

@@

%{% A SUMMARY
%=A summary modified/answers in cover letter (finish the first page) {
We re-wrote the Introduction with the studies of TCGA database according to the suggestion by reviewer\#2.
%[introduction] ok
%Answer 2-6 minor2 (how to study TCGA)
We introduced an independent HNSCC dataset (GSE65858) to provide more cases and evidence for supporting our biomarker candidates. The Results, Materials and Methods have included this information.
%[results] ok Answer 2-3 (GSE65858 then final 3 candidates)
We modified the Discussions about sample size, sliding window method, removal of "unclean data" statement according to the suggestion by reviewer\#2.
%[discussions] ok
%Answer 2-3 (sample size, effect size, pvalueTex cutoff of NDFIP1,  and P value)
%purpose of sliding window (ok 提 一下at  2-6 minor3)
%Answer 2-6 minor3 (In line 154 paragraph, what does "unclean data")
And the 'holistic cancer care" was also modified according to the suggestion by reviewer\#1.
%Answer 1-2 (holistic) figure 5
We added the description of FDR correction and Cox modeling in the Materials and Methods according to the suggestion by reviewer\#2.
%[materials and methods] ok
%Answer 2-1 (cutoff finding), replaced a new Figure 5 %(Figure_4_CAMK2N1_IL19_FCGBP.pdf)
%Answer 2-4 (Cox regression)
%Answer 2-3 (GSE65858)
%}
We modified Figure 1 and 2 according to the suggestion by reviewer\#2.
And new Figure 3, 4, 5 ,Table 1 and 2 was made for the updated results from GSE65858.
We also added new supplementary Figure S1.
%"Are the conclusions supported by the results?
%We provide more evidence by additional analysis of TCGA and GEO databases. %Moreover, we reviewed literature that supports the prognostic impact of these candidate genes.
%, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 
%to provide more evidence from the significant literature review.
And all our responses to reviewers' comments are in the following pages.

@@

We also think that the sliding-window selection of cutoffs would capture more genes whose \textit{P} values just reach the significant level (\textit{P}=0.05).
%http://bioinformatica.mty.itesm.mx:8080/Biomatec/SurvivaX.jsp run TCGA2016 in median (median cutoff; not case number 50\% 50\%)
%=> defense: 
%% *** 準備一張 20 candidates: accumulated \textit{P}-value plots 來(like Figure 4: (Please see supplementary Figure SXXX))
%說明，其實這些 P values 不論 50% cut or 70% 幾乎都 far less than 0.05
% file: 1453 Feb 15 2020 ./intermediate_data/HNSCC_OS_marginSFP_pvalueBonferroni_KM_candidate_cox.Rda => candidate_sample
%[1] "HNSCC_OS_marginS_pvalueBonferroni_sorted"   
%[2] "HNSCC_OS_marginFree_pvalueBonferroni_sorted"
%[3] "HNSCC_OS_marginPlus_pvalueBonferroni_sorted"
However, according to the results of sliding-window cutoff finding, the preliminary biomarkers have FDR-corrected \textit{P} values from \num{1e-4} to 0.04 which have been grouped by cutoffs between 50\% and 70\% quantile (Please see Figure \ref{fig:figure4}; it is also shown in manuscript as updated "Figure 5" for top 3 candidate biomarkers, CAMK2N1, CALML5, and FCGBP).
Moreover, the gene NDFIP1, one of our 20 preliminary candidates, has a \textit{P} value (around $0.05$) at 50\% quantile cutoff, achieving a \textit{P} value of \num{2.62e-6} at 70\% quantile cutoff (please see Figure \ref{fig:pvaluePlot_NDFIP1}, and also in 
supplementary figure S1). After the FDR correction, NDFIP1 still has \textit{P} value of \num[round-precision=3, round-mode=figures,
scientific-notation=true]{0.0001074233}.
%Rplot_pvaluePlot_NDFIP1.pdf
%  to find cases_OS outside of range 180-220 (== cutoff not at median)
%# pvalue plot as 倒V字形 "^" or W p_OS pvalues plots (with local minials)
% # 99 genes have one p_OS >= 0.05, in OS_pvalueTex005
%# 3641 genes have one p_OS >= 0.02, in OS_pvalueTex002
%# special case: HNSCC_survivalAnalysis_marginS_NDFIP1.xlsx
%# NDFIP1 (within our 20 preliminary candidates), 
In those \textit{P}-value plots, we could see that the sliding-window selection of cutoff finding might collect more potential candidates (\textit{P} values far less than $0.001$) for further Cox's modeling.
%Some useful biomarkers might be kick-out prematurely in "median cutoff" of survival analysis.
Indeed, it needs to be validated by the other independent cohort.
